A survey of HTTP caching options on the open Web

### 2015-01-12 sanity/paper1.tex
fix all cites
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@966 43ef1190-90fd-4dd7-a769-d0121f02b80e

The SPARQLES survey\todo{ref} has recorded the availability of SPARQL
endpoints registered in the datahub.io portal, and found that many of
them have ceased to operate. We used their list of SPARQL endpoints as
of 2014-11-17, and filtered out those deemed unresponsive by
them. This resulted in a list of 312 endpoints.

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014\todo{ref} dataset
consisted of a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps, manually inspecting the result between
each step. The details of this process is given in
Appendix~\ref{app:reduction}.

@@

This results in an NQuads file per host, which is then loaded into a
Virtuoso-based SPARQL Endpoint for analysis by using the statistics
system R\todo{ref}.

@@

In Figure\todo{figure with freshness breakdown}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification\todo{ref} also notes that the
statistics are considered estimates.

@@

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In Figure\todo{add all
  heuristics figure}, we see that the distribution of lifetimes are
radically different from the case in Figure\todo{ref fig:allhard}. In
this case, we may cache many resources for months. Only a handful of
resources had changed in the last minutes. Since this is based
on actual times since last modifications, this suggests that many
resources should have had explicit cache headers with very long
lifetimes. This is supported by DyLDO\todo{ref}, which concludes that:
\begin{quote}
[...] We found that 62.2\% of documents didn’t change over the six
months and found that 51.9\% of domains were considered static.
\end{quote}
This agrees well with that 60\% of the simple heuristic lifetimes are
in the month range.

@@

To allow generation and validation of \httph{Last-Modified} and
\httph{ETag} headers, DBMS authors should make sure it is much cheaper
to retrieve the modification time of any subgraph, than to retrieve
the subgraph itself. This would be a great improvement for
RFC7232-based caching, when revalidation is required. It would also
help simple heuristic based caching.\todo{ref kasei on mtime}.

@@

@@

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{3cm} | p{5cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge Architecture Specification\todo{ref} & Draft
to allow more fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\todo{ref}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww\todo{ref}  & Header inserted by User
Agent to give details about problems with the download \\ \hline

>>>>

The SPARQLES survey\cite{buil2013sparql} has recorded the availability
of SPARQL endpoints registered in the datahub.io portal, and found
that many of them have ceased to operate. We used their list of SPARQL
endpoints as of 2014-11-17, and filtered out those deemed unresponsive
by them. This resulted in a list of 312 endpoints.

@@

To examine as many different implementations and hosts as possible, we
noted that the Billion Triple Challenge 2014 \cite{btc-2014} dataset
consisted of a 4~GTriple corpus of spidered Web data. To compile a
list of interesting candidates to further examine, we performed a
series of data reduction steps, manually inspecting the result between
each step. The details of this process is given in
Appendix~\ref{app:reduction}.

@@

This results in an NQuads file per host, which is then loaded into a
Virtuoso-based SPARQL Endpoint for analysis by using the statistics
system R\cite{kn:r}.

@@

In Figure\todo{figure with freshness breakdown}, we have broken this
up by the type of resource that was accessed, i.e. SPARQL endpoints,
vocabularies, dataset descriptions or unclassified information
resources. First, we note that it seems like the distribution of
freshness lifetime is quite different for the different types, an
observation that is also supported by a similar hypothesis test as
above, with a \pvalue = 0.00001. We also note that it is often
prohibited to cache dataset descriptions. This is odd, since
statistics about datasets is usually costly to compute and should be
cached. The VoID specification \cite{voidnote} also notes that the
statistics are considered estimates.

@@

We were able to compute a heuristic lifetime for 554 resources, a
larger number than standards-compliant resources. In Figure\todo{add all
  heuristics figure}, we see that the distribution of lifetimes are
radically different from the case in Figure\todo{ref fig:allhard}. In
this case, we may cache many resources for months. Only a handful of
resources had changed in the last minutes. Since this is based
on actual times since last modifications, this suggests that many
resources should have had explicit cache headers with very long
lifetimes. This is supported by DyLDO\cite{dyldo2}, which concludes that:
\begin{quote}
[...] We found that 62.2\% of documents didn’t change over the six
months and found that 51.9\% of domains were considered static.
\end{quote}
This agrees well with that 60\% of the simple heuristic lifetimes are
in the month range.

@@

To allow generation and validation of \httph{Last-Modified} and
\httph{ETag} headers, DBMS authors should make sure it is much cheaper
to retrieve the modification time of any subgraph, than to retrieve
the subgraph itself. This would be a great improvement for
RFC7232-based caching, when revalidation is required. It would also
help simple heuristic based caching. Research in that direction has
been published in \cite{kaseicache}.

@@

\bibliographystyle{plain}
%\bibliographystyle{abbrv}
%\bibliographystyle{jbact}
%\bibliographystyle{splncs03}
\bibliography{webarch,data,rfc,hypermedia,dynamicity}

@@

\begin{table}
\caption{Recorded HTTP headers}\label{tab:headers}
 \begin{tabular}{ | l |  p{3cm} | p{5cm} |}
    \hline
    Header & Reference & Description \\ \hline
\httph{Age} & RFC7234 & When obtaining response from a cache, the number of
seconds since validation \\ \hline
\httph{Cache-Control} & RFC7234 & Header used for a variety of directives \\ \hline
\httph{Expires} & RFC7234  & Gives the date/time after which the
   response is considered stale. \\ \hline
\httph{Pragma} & RFC7234 & Archaic HTTP 1.0 header  \\ \hline
\httph{Warning} & RFC7234  & For additional information about possible incorrectness \\ \hline
\httph{Content-Type} & RFC7231 & To select the correct parser \\ \hline
\httph{If-None-Match} & RFC7232  & Request header to check if
                                   \httph{ETag} has changed   \\ \hline
\httph{If-Modified-Since} & RFC7232  & Request header to check if
                                   \httph{Last-Modified} has changed    \\ \hline
\httph{Last-Modified} & RFC7232 & When the resource was last modified \\ \hline
\httph{ETag} & RFC7232 & An opaque validator to check if the resource
has changed  \\ \hline
\httph{X-Cache} &  & Inserted by some caches to indicate cache status \\ \hline
\httph{Date} & RFC7231 & The time of the message. Used in conditional requests
and heuristics \\ \hline
\httph{Surrogates} & Edge Architecture Specification\cite{edgearch} & Draft
to allow more fine-grained control for proxies. \\ \hline
\httph{Client-Aborted} & libwww\todo{ref}  & Header inserted by User
Agent to indicate that it aborted the download \\ \hline
\httph{Client-Warning} & libwww\todo{ref}  & Header inserted by User
Agent to give details about problems with the download \\ \hline
